Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-23 paper_jasa.tex
some comments added

\noindent Ideally, the visual test statistic is defined using the grammar of graphics \citep{wilkinson:1999,hadley:2009}, consisting of type, and specification of aesthetics, necessary for complete reproducibility. The visual test statistic is compared with values $T(y_0)$ using a lineup, which is defined as:

@@

\begin{dfn}\label{dfn:test}
The \textbf{test} is defined to be 
\begin{itemize}\itemsep-3pt
\item \textbf{Reject} $H_0$ if the observer selects the observed data plot, and
\item \textbf{Fail to reject} $H_0$ if the observer selects a null plot.
\end{itemize}
\end{dfn}

The number of plots in the lineup, $m$, controls the Type I error. The probability of choosing any one of the plots is $1/m$, so the chance of making a wrong decision by chance is $1/m$. Classically, Type II error is the probability of failing to reject $H_0$ when it is not true, which is more difficult to quantify.

>>>>

\noindent Ideally, the visual test statistic is defined (\red{should it be constructed/plotted/drawn?}) using the grammar of graphics \citep{wilkinson:1999,hadley:2009}, consisting of type, and specification of aesthetics, necessary for complete reproducibility. The visual test statistic is compared with values $T(y_0)$ using a lineup, which is defined as:

@@

\begin{dfn}\label{dfn:test}
The \textbf{(\red{Visual}) test} is defined to be 
\begin{itemize}\itemsep-3pt
\item \textbf{Reject} $H_0$ if the observer selects the observed data plot, and
\item \textbf{Fail to reject} $H_0$ if the observer selects a null plot.
\end{itemize}
\end{dfn}

The number of plots in the lineup, $m$, controls the Type I error. The probability of choosing any one of the plots is $1/m$, so the probability of making a wrong decision by chance is $1/m$. Classically, Type II error is the probability of failing to reject $H_0$ when it is not true, which is more difficult to quantify.
